Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-04-27 ms.tex
more on subpixel level of crosshatch

>>>>

The crosshatch structure of the detectors extends down to the subpixel level, so it may not be fully corrected with a flat field division.
This sub-pixel structure has been imaged with microscopy \citep{shapiro2018crosshatch}.
The width of the structures can be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
